Warming Degrees and Flowering Trees

### 2025-04-04 paper/paper.qmd
Refactor code structure and improve readability in Jupyter notebooks

The relationship between sakura blooming date and other factors was first examined in depth. A notable amount of scholarship addresses the relationship between different variables and and the flowering dates of sakura, from humanistic cultural studies perspectives ranging to scientific plant biology, phenological modeling, and climatology studies.

@@

@@

>>>>

The Japanese tradition of Hanami has become a cultural juggernaut for the nation, even spreading globally. Its cultural significance cannot be understated, which underscores the importance of being able to predict when the blooming season for cherry blossoms will begin. The cultural significance of Hanami is not only a historic and cultural cornerstone, but has also become an economic one.
Around the 8th century, sakura flowering had begun to assume special importance. Anthropologists note that in early Japanese agrarian society, cherry blossoms were closely tied to rice farming – the bloom of the cherries was believed to forecast the year’s rice harvest @CITEHanyan. Festivals would be conducted at shrines and the imperial court, where the emperor would offer prayers under blooming cherries for a bountiful autumn harvest @CITEHanyan. Sakura began to symbolize agrarian prosperity and “life power,” intimately linking Japanese livelihoods with seasonal rhythms of blooming @CITEHanyan. Furthermore, the blossoms started to be seen as extensions of imperial authority – one analysis notes that the emperor’s spiritual responsibility for the nation “extended ‘as far as cherries are in bloom’” @CITEHanyan, demonstrating how the flower was initially imbued with the cultural significance it holds now.

Cherry blossoms continued to ingrain themselves into Japanese culture. While Hanami was originally an aristocratic pastime, initiatives by Japanese leaders evolved into a widespread tradition shared by all classes lup.lub.lu.se. Historical records indicate feudal lords and government officials would encourage their subjects to participate in planting trees as well as the viewing of their bloom lup.lub.lu.se. Hanami gradually became widespread, and had begun to influence Japanese art and culture substantially. An exhibit and the Library of Congress reveals the extent to this influence, showing through several eras and lords that the cherry blossom remained a common motif to symbolize seasonal joy and life’s fleeting pleasures for the Japanese people @CITEcongress. There was also religious significance to the cherry blossom, due to the influence of Buddhism infused the practice of Hanami as a reminder of life’s impermanence @CITEHanyan. Thus, by the early modern period, the cultural symbolism of sakura had acquired multiple layers: on one hand, it represented renewal, beauty, and communal celebration, and on the other, a poignant reminder of mortality @CITEHanyan – regardless of its artistic symbolism, the widespread appreciation of the cherry blossom bloom had cemented the season as a cultural cornerstone.

This leads us to current day Japan. Sakura season is now a major economic and touristic phenomenon. The season is promoted by travel agencies, rail companies, and local tourism boards both domestically and internationally. Famous cherry blossom spots are must-see destinations each spring. As noted in @CITEjapantimes - “Hanami... has been a nationwide event for a long time in Japan. The beautiful sakura has now become a tourism asset, attracting foreign tourists”. Data highlights the sheer economic scale of the season: the estimated the economic effect of hanami in 2024 was ≈$7.7 billion USD in Japan, nearly double the previous year’s figure @CITEjapantimes. The economic impact of the cherry blossom is in no small part due to its cultural and historical significance in Japanese culture. This brings us to the importance of modelling this data. The surge of visitors to parks and landmarks during peak bloom sometimes creates logistical challenges, as vendors and tourist destinations must prepare for the influx of visitors domestic and international. Without adequate time to prepare for Hanami, locales risk being flooded which would cause a disruption to the revenue that Japan has come to expect @CITEmoriuchi.

To summarize, the tradition of Hanami in Japan can be considered timeless. It’s roots in agarian traditions has also cemented a practice of recording the data around cherry blossom blooming, due to its ties to the harvest and perceived prosperity. It’s gradual establishment in Japanese art and culture has also made in a juggernaut in that regard, cementing its place as a staple in Japanese culture. Despite no longer needing to track the blossoming for the harvest, a new necessity for the data collection has arisen: economic benefit. With ever changing circumstances due to climate change, accurately predicting the Hanami period is more important than ever, as the sheer scale of the event for Japan culturally and economically requires substantial preparation for the celebrations to run smoothly. Otherwise, Japan could risk losing reliable revenue or potentially damage its reputation as a global cultural powerhouse.

The relationship between sakura blooming date and other factors was next examined in depth. A notable amount of scholarship addresses the relationship between different variables and and the flowering dates of sakura, from humanistic cultural studies perspectives ranging to scientific plant biology, phenological modeling, and climatology studies.

@@

::: {#refs}
:::

@@

\appendix
